Hydrodynamics and rheology of an adhesive vesicle doublet

### 2019-02-10 vesicle_code/docs/adhesion/adhesion.tex
working on fig 14/15
fixed up figure 14

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions.
Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
suspended inside of a larger vesicle.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.  In
Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
(left) and adhesion (right) of the final equilibrium configuration.
Both the vesicle shape, tension, and adhesion qualitatively agree with
our doublet results.  In particular, the interior vesicles form a flat
contact region with a large negative tension.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
  \caption{\label{fig:relaxationManyVes} Five vesicles suspended inside
  a large vesicle.  The background flow is quiescent, the adhesion
  length scale is $\delta = 0.4$, and the Hamaker constant is
  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
  equilibrium configuration.}
\end{figure}

@@

\begin{figure}[htp]
\centering
\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesTension.png}
\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesAdhesion.png}
\caption{\label{fig:relaxationManyVesAdhesionTension} The tension ({\em
left}) and adhesion force ({\em right}) of the final configuration from
Figure~\ref{fig:relaxationManyVes}.  Along the bounding vesicle, the
tension is largest and the adhesion is smallest in the regions that are
well-separated from the interior vesicles.  Similar to other
simulations, the interior vesicles are relatively flat and have a large
negative tension in the contact regions.}
\end{figure}

>>>>

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions.
Figure~\ref{fig:relaxationManyVes} shows an initial condition of five vesicles
suspended inside of a larger vesicle, and the configuration and
streamlines at an intermediate configuration.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.   We also plot the tension (thrid) and
adhesion (fourth) of the final equilibrium configuration.  Both the
vesicle shape, tension, and adhesion qualitatively agree with our
doublet results.  In particular, the interior vesicles form a flat
contact region with a large negative tension.

%\begin{figure}[htp]
%  \centering
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot01.pdf}
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot02.pdf}
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot03.pdf}
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot04.pdf} \\
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot05.pdf}
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot06.pdf}
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot07.pdf}
%  \includegraphics[width=0.24\textwidth]{figs/relaxationManyVes_Snapshot08.pdf}
%  \caption{\label{fig:relaxationManyVes} Five vesicles suspended inside
%  a large vesicle.  The background flow is quiescent, the adhesion
%  length scale is $\delta = 0.4$, and the Hamaker constant is
%  $\mathcal{H} = 0.7$.  At the final snapshot, the suspension is near an
%  equilibrium configuration.}
%\end{figure}

\begin{figure}[htp]
\centering
\includegraphics[height=0.24\textwidth,trim={10cm 0cm 10cm 0cm},clip]{figs/relaxationManyVesInitialCondition.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesStreamlines.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 1cm 0cm},clip]{figs/relaxationManyVesTension.png}
\includegraphics[height=0.24\textwidth,trim={2cm 0cm 2cm 0cm},clip]{figs/relaxationManyVesAdhesion.png}
\caption{\label{fig:relaxationManyVes} Five vesicles in a quiescent flow
suspended in a bounding vesicle.   All vesicles are interacting through
an adhesion potential with Hamaker constant $\mathcal{H} = 0.7$ and
separation distance $\delta = 0.4$.  From left to right, the plots are
the initial condition, streamlines and an intermediate time, tension at
the steady-state configuration, and the adhesion force projected onto
the outward unit normal at the steady-state configuration.  Along the
bounding vesicle, the tension is largest and the adhesion is smallest in
the regions that are well-separated from the interior vesicles.  Similar
to other simulations, the interior vesicles are relatively flat and have
a large negative tension in the contact regions.}
\end{figure}

@@
